### 2016-09-26 doc/publications/plos16/plos16.tex

\begin{table}[!ht]
\centering
\caption{
{\bf Time in seconds to build random forest of 100
  trees on 128 CPU cores with varying numbers of variables and samples.}}
\begin{tabular}{|l|l||l|l|l|l|l|}
\hline
\multicolumn{2}{|l||}{\multirow{2}{*}{}}               & \multicolumn{5}{c|}{Number of variables}  \\
\cline{3-7}
\multicolumn{2}{|l||}{}                                & \bf{150,000} & \bf{500,000} & \bf{2,500,000}  & \bf{10,000,000} & \bf{50,000,000} \\
\hline                                                            
\multirow{4}{*}{Number of samples}                          & \bf{1000} &  21.6 & 26.7 & 59.8 & 133.5 & 668.8 \\
                                                            & \bf{5000} & 45.7 & 71.9 & 186.2 & 729.3 & 2887.4 \\
                                                            & \bf{10000} & 70.2 & 120.2 & 397.3 & 2237.8 & 5747.8 \\
\hline
\end{tabular}
\begin{flushleft} 
\end{flushleft}
\label{table10}
\end{table}

\begin{table}[!ht]
\centering
\caption{
{\bf Time in seconds to build random forest of 100
  trees with specified mtry fraction using given number of CPU cores.}}
\begin{tabular}{|l|l||l|l|l|l|}
\hline
\multicolumn{2}{|l||}{\multirow{2}{*}{}}                   & \multicolumn{4}{|c|}{Number of CPU cores}  \\
\cline{3-6}
\multicolumn{2}{|l||}{}                                               & \bf{16} & \bf{32}      & \bf{64}      & \bf{128}  \\
\hline
\multirow{4}{*}{mtry (fraction)}                            & \bf{0.10} & 708.3  & 340.0  & 186.0 & 134.5 \\
                                                            & \bf{0.25} & 1134.9 & 535.0  & 270.8 & 179.6 \\
                                                            & \bf{0.50} & 1724.1 & 856.6  & 428.7 & 243.8 \\
                                                            & \bf{0.80} & 2313.5 & 1125.7 & 569.1 & 364.6 \\

\hline
\end{tabular}
\begin{flushleft} 
\end{flushleft}
\label{table10}
\end{table}

>>>>

\begin{table}[!ht]
\centering
\caption{
{\bf Time in seconds to build random forest of 100
  trees on 128 CPU cores with varying numbers of variables and samples.}}
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{\multirow{2}{*}{}}               & \multicolumn{5}{c|}{Number of variables}  \\
\cline{3-7}
\multicolumn{2}{|l|}{}                                & \bf{150,000} & \bf{500,000} & \bf{2,500,000}  & \bf{10,000,000} & \bf{50,000,000} \\
\hline                                                            
\multirow{4}{*}{Number of samples}                          & \bf{1000} &  21.6 & 26.7 & 59.8 & 133.5 & 668.8 \\
                                                            & \bf{5000} & 45.7 & 71.9 & 186.2 & 729.3 & 2887.4 \\
                                                            & \bf{10000} & 70.2 & 120.2 & 397.3 & 2237.8 & 5747.8 \\
\hline
\end{tabular}
\begin{flushleft} 
\end{flushleft}
\label{table10}
\end{table}

\begin{figure}[tbhp]
\begin{tabular}{ll}
a)& b)\\
\includegraphics[totalheight=6cm]{./figs/nsamples_nvars.png} & 
\includegraphics[totalheight=6cm]{./figs/nvars_nsamples.png} \\
\end{tabular}
\captionof{figure}{{\bf Scalablity of the Wide Random Forest on synthetic datasets with varying number of samples and variables.} 
   {\bf a)} Time in seconds to build 100 trees for differnet mtry fractions. 
   {\bf b)} Number of trees build per hour when using a growing number of CPU cores.}
\label{figure:synth}
\end{figure}

\begin{table}[!ht]
\centering
\caption{
{\bf Time in seconds to build random forest of 100
  trees with specified mtry fraction using given number of CPU cores.}}
\begin{tabular}{|l|l||l|l|l|l|}
\hline
\multicolumn{2}{|l|}{\multirow{2}{*}{}}                   & \multicolumn{4}{c|}{Number of CPU cores}  \\
\cline{3-6}
\multicolumn{2}{|l|}{}                                      & \bf{16}   & \bf{32}  & \bf{64}    & \bf{128} \\
\hline
\multirow{4}{*}{mtry (fraction)}                            & \bf{0.10} & 708.3  & 340.0  & 186.0 & 134.5 \\
                                                            & \bf{0.25} & 1134.9 & 535.0  & 270.8 & 179.6 \\
                                                            & \bf{0.50} & 1724.1 & 856.6  & 428.7 & 243.8 \\
                                                            & \bf{0.80} & 2313.5 & 1125.7 & 569.1 & 364.6 \\
\hline
\end{tabular}
\begin{flushleft} 
\end{flushleft}
\label{table10}
\end{table}
